Relative parabolic factorizations of Chevalley groups

### 2015-08-31 congrsubgr-boundgen.tex
Partially rewritten DV section

\begin{lemma}\label{lemma:srRI1_width} In the assumptions of Lemma~\ref{lemma:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$. \end{lemma}
\begin{proof}
Take an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$. 
Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
 (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
and the estimate follows. \end{proof}

>>>>

\begin{lemma}\label{lemma:srRI1_width} In the assumptions of Lemma~\ref{lemma:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$. \end{lemma}
\begin{proof}
Take an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$. 
Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
 (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
and the estimate follows. \end{proof}

### 2015-08-31 dennis-vaserstein.tex
Slight changes in the notation; further reorganization
Tiny typography fix in DV statement
Partially rewritten DV section

Let $\Phi$ be an irreducible root system of rank $\ell$.
Let $r$, $s$ be two distinct indices $1\leq r,s \leq \ell$.
From Levi decomposition it follows that
\begin{multline*}
\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
= \U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = \\
= \EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I).
\end{multline*}
Denote by $A_{rs}$ any of the equal subsets from the previous formula.

The main result of this subsection is the following theorem which is a relative analogue of Dennis---Vaserstein decomposition~\cite[Theorem~2.5]{St78}.

\begin{thm}\label{thm:DennisVaserstein}
The relative elementary subgroup $\E(\Phi, R, I)$ coincides with the subset $A_{rs}$ under the following assumptions on $I$:
\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
\Phi = \rA_\ell, \rB_\ell,\ \ell\geqslant 2, & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-1; \\     
\Phi = \rD_\ell,\ \ell\geqslant 4,           & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-2; \\ 
\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 2), & \sr(I) \leqslant \ell-3; \\ 
\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 1), & \asr(I)\leqslant \ell-2.
\end{array}\]
\end{thm}
The proof of Theorem~\ref{thm:DennisVaserstein} occupies the rest of this section.
Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\},\quad L_{rs}= \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} = A_{rs} \right\}. \]

It is easy to see that $N_{rs}$ normalizes $L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq A_{rs}^g \subseteq A_{rs}.$$

\begin{lemma}\label{lemma:dv_unipotent}
For any $1\leq i\leq n$ the following statements hold (together with their analogues for $\Phi^-$).
\begin{enumerate} 
\item $\U(\Phi^+, I) = \X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot \X_{\alpha\ssub{i}}(I)$.
\item For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
\item $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{i}}(I) \cdot \X_{-\alpha\ssub{i}}(I)$.
\end{enumerate}
\end{lemma}
\begin{proof}
 The first two statements easily follow from Chevalley commutator formula while the third one is a formal consequence of the first two.
\end{proof}

The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of the absolute Dennis--Vaserstein decomposition.
\begin{lemma}\label{lemma:Stein_reduction}
Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ with the following properties:
\begin{enumerate}[label=(\alph*)] 
 \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$
 \item\label{stein_cond2} One has $\X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
\end{enumerate}
Then $\X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s \subseteq N_{rs}.$
\end{lemma}
\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
From assumption~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} together imply
\begin{multline*}
A \subseteq \U(\Phi^+\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I).
\end{multline*}
Now applying Lemma~\ref{lemma:dv_unipotent} we get the following inclusions:
\begin{align*}
& A^{\X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{\X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A; \\
& \X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A.
\end{align*}
To prove the second part of the statement observe first that $\EP_s$ is generated by $\X_{\alpha\ssub{i}}$ for $1\leqslant i\leqslant n$ and $\X_{-\alpha\ssub{i}}$ for $i\neq s$.
%TODO: Find proper reference for this fact
We have just shown that $\X_{-\alpha_r}\subseteq N_{rs}$.
On the other hand, inclusions $\X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $\X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
\end{proof}

@@

%TODO: PICK AS L_r!!!
Let $\widetilde{L_r}$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
In any of  the specified cases the assumption on $I$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in \widetilde{L_r}$.
This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) \widetilde{L_r}. \]
To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
\[ \X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]

From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
Notice that in view of Theorem~\ref{theorem:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
\begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
\item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
Since $\EP_s \subseteq N_{rs}$, the inclusions for the first family of elements follow from those for the second one.
We already know that $\U(\Phi^+, I) \subseteq L_{rs}$, hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.

Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $\X_\alpha(I)$, $\alpha\in \Delta_s$
and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.

%Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$, hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
have the same $s$-shape and
%(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
hence by Lemma~\ref{lemma:abs} are interchanged by the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
%By the same argument as above we get that $W(\Delta_s)$.
Since $\X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
This completes the proof of the theorem for $\Phi\neq \rB_\ell$.

In the case $\Phi=\rB_\ell$ we have to show additionally that $\X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
denotes the maximal short root of $\rB_\ell$.
By Chevalley commutator formula we have
\[ x_{-{\alpha^<_{\mathrm{max}}}}(s) = x_{-1,0}(s) = x_{1,-2}(s) \cdot x_{-1,-2}(-s)^{x_{-2, 0}(-1)} \cdot x_{-1, 2}(\xi),\ s\in I. \]
On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $\X_{-1,-2}(I), \X_{-1, 2}(I) \subseteq L_{rs}$.
This concludes the proof of the theorem.
\end{proof}

>>>>

Let $\Phi$ be an irreducible root system of rank $\ell$.
For an integer $1 \leq s \leq \ell$ consider the following two subgroups of $\E(\Phi, R)$:
$$\EP_s(R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R),\ \EP_s(R, I) = \E(\Delta_s, R, I) \cdot \U(\Sigma_s, I).$$

Let $1\leq r,s \leq \ell$ be two distinct integers.
From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
\begin{multline*}
\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
= \U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = \\
= \EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I).
\end{multline*}
\begin{dfn}
 Denote by $A_{rs}$ any of the above equal subsets.
 We call the decomposition of the form $\E(\Phi, R, I) = A_{rs}$ the {\it relative Dennis---Vaserstein} decomposition.
\end{dfn}

The main result of this subsection is the following theorem which is a relative version of \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
\begin{thm}\label{thm:DennisVaserstein}
The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition under the following assumptions on $I$.
\[\begin{array}{|c|l|c|l|}
\hline \Phi & s & r & \text{ring condition} \\ \hline
\rA_\ell, \rB_\ell,\ \ell\geqslant 2 & 1 & \ell & \sr(I) \leqslant \ell-1 \\     
\rC_\ell,\ \ell \geqslant 2          & 1 & \ell & \sr(I) \leqslant \ell-1 \\
\rD_\ell,\ \ell\geqslant 4           & 1 & \ell & \sr(I) \leqslant \ell-2 \\ 
\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2 \\
\rE_\ell,\ \ell=6,7             & \ell & 2 & \sr(I) \leqslant \ell-3 \\ 
\rE_\ell,\ \ell=6,7             & \ell & 1 & \asr(I)\leqslant \ell-2 \\ \hline
\end{array}\]
\end{thm}
%Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
%This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
%On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
%Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
Consider the following two subsets of $\E(\Phi, R)$:
\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\}, \quad
   L_{rs}=  \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} \subseteq A_{rs} \right\}. \]

It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.e. ${L_{rs}}^{N_{rs}} \subseteq L_{rs}$. 
Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} = g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g = A_{rs}.$$

\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$.
\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
\end{thmlist} \end{lemma}
\begin{proof} The first two statements easily follow from Chevalley commutator formula~\ref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}

%The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78}
%for the proof of the absolute Dennis--Vaserstein decomposition.

\begin{lemma}\label{lemma:Stein_reduction}
Assume that there exists a subset $B \subseteq \E(\Delta_r, R, I)$ satisfying the following assumptions:
\begin{enumerate}
 \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B.$
 \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^B \subseteq \EP_s(R, I).$
\end{enumerate}
Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s(R) \subseteq N_{rs}.$
\end{lemma}
\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
From the first assumption of the lemma it follows that $A_{rs}=A$.
On the other hand, by the second assumption we have
\begin{multline*} X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
 X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
 \subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) \subseteq 
 B \cdot \EP_s(R, I). \end{multline*}
Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
\begin{equation} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation}
Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
\begin{equation} \label{rel:linv} X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) = A. \end{equation}
Since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we also get that:
\begin{equation} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \end{equation}

To prove the second part of the statement observe first that $\EP_s(R)$ is generated by $X_{\alpha\ssub{i}}(R)$ for $1\leqslant i\leqslant n$ and $X_{-\alpha\ssub{i}}(R)$ for $i\neq s$.
%TODO: Find proper reference for this fact
From \ref{rel:ninv} it follows that $X_{-\alpha_r}(R)\subseteq N_{rs}$.
On the other hand, inclusions $X_{\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $X_{-\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
\end{proof}

@@

%TODO: PICK AS L_r!!!
Let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
In any of  the specified cases the assumption on $I$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in B$.
This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) B. \]
To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]

From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
Notice that in view of Theorem~\ref{thm:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
\begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
\item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
Since $\EP_s \subseteq N_{rs}$, the inclusions for the first family of elements follow from those for the second one.
We already know that $\U(\Phi^+, I) \subseteq L_{rs}$, hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.

Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$
and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.

%Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$, hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
have the same $s$-shape and
%(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
hence by Lemma~\ref{lemma:abs} are interchanged by the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
%By the same argument as above we get that $W(\Delta_s)$.
Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
This completes the proof of the theorem for $\Phi\neq \rB_\ell$.

In the case $\Phi=\rB_\ell$ we have to show additionally that $X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
denotes the maximal short root of $\rB_\ell$.
By Chevalley commutator formula we have
\[ x_{-{\alpha^<_{\mathrm{max}}}}(s) = x_{-1,0}(s) = x_{1,-2}(s) \cdot x_{-1,-2}(-s)^{x_{-2, 0}(-1)} \cdot x_{-1, 2}(\xi),\ s\in I. \]
On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.
This concludes the proof of the theorem.
\end{proof}
